---
title: "Historic Hudson James Bay Coast Highwater and Hydrometric Variables"
output: html_document
---

```{r setup, include=FALSE}

#load libraries
library(here)
library(readxl)
library(weathercan)
library(kiwisR)
library(tidyhydat)
library(conflicted)
library(tidyverse)
library(zoo)
library(rforecastca)
library(plotly)
library(crosstalk)
library(lubridate)
library(DT)
library(tidyhydat)
library(leaflet)
library(rclimateca)

conflict_prefer("filter", "dplyr")
conflict_prefer("here", "here")
conflict_prefer("yday", "lubridate")
conflict_prefer("month", "lubridate")
conflict_prefer("year", "lubridate")

#source functions

source(here::here("scripts", "NRT interactive graphing functions.R"))

```

# {.tabset}

## Station Map {.tabset}

```{r Station_Map, warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

create_sta_map()

```



## NAEFS Forecast 

```{r NAEFS, warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

plot_naefs_forecast("Moosonee")

```

Information on the North American Ensemble Forecast System can be found at the following link:

https://weather.gc.ca/ensemble/naefs/index_e.html

## Moose River {.tabset}

### Flow and Level

#### Flow

***Uncorrected flow data are not suitable for comparison to previous corrected data

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

mse_04LG004_q()

```

#### Level

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

mse_04LG004_lvl()

```

### Climate

#### Degree Days of Freezing

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

fdd_plot()

```

#### Snow Depth

***According to Ken there is an issue with the Moosonee Climate station snow instrument so use with caution

_______________________________________________________________________________

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

sd_plot("XZC")

```

#### Positive Degree Days of Warming

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

pdd_plot()

```

#### Cumulative Rain

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

cum_rain_plot()

```

<!-- #### Snow Depth Depletion -->

<!-- ```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12} -->

<!-- depl_plot() -->

<!-- ``` -->

<!-- #### Cumulative Rain Plus Snow Depth Depletion -->

<!-- ```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12} -->

<!-- cum_rain_depl_plot() -->

<!-- ``` -->

### Moose Headwater Snow Depths

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

# look at Nagagami (WNZ), Timmins (YTS) and Kapuskasing (XKA) Climate stations

sd_plot("XKA")

sd_plot("WNZ")

sd_plot("YTS")

```

## Albany River 

### Flow

***Uncorrected flow data are not suitable for comparison to previous corrected data

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

alb_04HA001_q()

```

### Level

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

alb_04HA001_lvl()

```

## Attawapiskat River 

***Uncorrected flow data are not suitable for comparison to previous corrected data

### Flow

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

att_04FC001_q()

```

### Level

```{r warning=FALSE,message=FALSE, echo=FALSE, fig.height=6, fig.width=12}

att_04FC001_lvl()

```
